\pkg{fitdistrplus}: An \proglang{R} Package for Fitting Distributions

### 2014-02-10 JSS/fitdistrplus/paper2JSS.Rnw
before resubmit
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/riskassessment@272 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The \proglang{R}  package \pkg{fitdistrplus} allows to easily fit distributions. 
Our main objective while developing this package was to provide tools for helping 
\proglang{R} users to fit distributions to data. 
We have been encouraged to pursue our work by feedbacks 
from users of our package in various areas as food or environmental risk assessment, epidemiology, ecology, 
molecular biology, genomics, bioinformatics, hydraulics, mechanics, financial and actuarial mathematics 
or operations research. Indeed, this package is already used by a lot of practionners and academics 
for simple MLE fits \citep{jaloustreetal11,saketal11,kochetal12,marquetouxetal12,nordan12,
scholletal12,suuronenetal12,varoetal12,mandletal13,mala2013,mala2013publi,nadarajahbakar2013,simoetal13,
westphalfitch13,wayland13,vianaetal13,wu13,staggeetal13,fiorellietal13,mukhopadhyay13,tikoleetal13,
voigtetal14}, 
for MLE fits and goodness-of-fit statistics 
\citep{tarnczi11,garcia12,bagariaetal12,benavidesetal12,breitbach12,poduje12,Pouillot10,vaninsky13}, 
for MLE fits and bootstrap \citep{croucheretal12,meheustetal12,orellanoetal12,telloetal12,hoelzeretal12,
prosseretal13,Zhang2013,lebaut13,Rigaux2014}, 
for MLE fits, bootstrap and goodness-of-fit statistics \citep{rebuge12,larrasetal13}, 
for MME fit \citep{luangkesornetal12,callauetal13,satoetal13}, 
for censored MLE and bootstrap \citep{lehaetal11,pouillotetal11,poulliotetal12,jongenburgeretal12,
commeauetal12,Kingetal2013,contrerasetal2013,duarte13,feng13}, 
for graphic analysing in \citep{anandetal12,rosa12}, 
for grouped-data fitting methods \citep{fusteinercostafreda12} 
or more generally \citep{busschaertetal10,brooksetal11,aktassjostrand11,bakos11,eling12,eikhermann12,
sosaetal2013,srinivasanetal2013,meyeretal13,Guillier2013471,Daelmanetal13,gustafssonetal13,
eiketal13,Wu2:2013,drakeetal2014}.

>>>>

The \proglang{R}  package \pkg{fitdistrplus} allows to easily fit distributions. 
Our main objective while developing this package was to provide tools for helping 
\proglang{R} users to fit distributions to data. 
We have been encouraged to pursue our work by feedbacks 
from users of our package in various areas as food or environmental risk assessment, epidemiology, ecology, 
molecular biology, genomics, bioinformatics, hydraulics, mechanics, financial and actuarial mathematics 
or operations research. Indeed, this package is already used by a lot of practionners and academics 
for simple MLE fits \citep{jaloustreetal11,saketal11,kochetal12,marquetouxetal12,
scholletal12,suuronenetal12,varoetal12,mandletal13,mala2013publi,nadarajahbakar2013,simoetal13,
westphalfitch13,wayland13,vianaetal13,wu13,staggeetal13,fiorellietal13,tikoleetal13,
voigtetal14}, 
for MLE fits and goodness-of-fit statistics 
\citep{tarnczi11,bagariaetal12,benavidesetal12,breitbach12,Pouillot10,vaninsky13}, 
for MLE fits and bootstrap \citep{croucheretal12,meheustetal12,orellanoetal12,telloetal12,hoelzeretal12,
prosseretal13,Zhang2013,Rigaux2014}, 
for MLE fits, bootstrap and goodness-of-fit statistics \citep{larrasetal13}, 
for MME fit \citep{luangkesornetal12,callauetal13,satoetal13}, 
for censored MLE and bootstrap \citep{lehaetal11,poulliotetal12,jongenburgeretal12,
commeauetal12,contrerasetal2013}, 
for graphic analysing in \citep{anandetal12}, 
for grouped-data fitting methods \citep{fusteinercostafreda12} 
or more generally \citep{busschaertetal10,eling12,
sosaetal2013,srinivasanetal2013,meyeretal13,Guillier2013471,Daelmanetal13,
eiketal13,Wu2:2013,drakeetal2014}.
